Data Cleaning

### 2025-12-09 Data Cleaning.Rmd
Changed column names for FeCl/polymer doses

```{r}
# Look at performance of a model that simply pulls previous year dose

@@

```{r}
df_lag_incdec |>
  rename(FeCl_dose = Ferric.chloride..mg.L,
         Polymer_dose = Cationic.Polimer..mg.L)

write.csv(df_lag_incdec, "RWAR_dosing_lag_incdec.csv")

>>>>

```{r}
# Look at performance of a model that simply pulls previous year dose
# not working

@@

```{r}
new_df <- df_lag_incdec |>
  rename(FeCl_dose = Ferric.chloride..mg.L,
         Polymer_dose = Cationic.Polimer..mg.L)

write.csv(new_df, "RWAR_dosing_lag_incdec.csv")
